---
title: "Assignment01"
author: "WenxinXie"
date: "2023-10-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1 Create a data frame

```{r}
animals<- c("Snake","Ostrich","Cat","Spider")
num_legs<- c(0,2,4,8)
animals_df<- data.frame(animals,num_legs)
print(animals_df)
```

## Q2 Check and delete objects

```{r}
rm(animals_df)
ls()
rm(num_legs)
rm(animals_df)
ls()

```

## Q3 Create a data frame in R Scripts

finished in R scripts.

## Q4 Create a data frame in R Markdown

finished in this R markdown.

## Q5 Matrix operations

5.1 Generate a sequence of numbers starting at 12 and decreasing to 2 in steps of -2.

```{r}
x_vect<- seq(12,2,by = -2)
x_vect
```

5.2 Convert the vector x vect into a matrix (with 2 rows and 3 coloumns) called X, using the matrix() function.

```{r}
X<- matrix(seq(12,2,by = -2),2,3)
X
```

5.3 Create a 2 by 2 matrix called Y consisting of a sequence of four numbers from 1-4.

```{R}
Y<- matrix(seq(4),2,2)
Y
```

5.4 Create another 2 by 2 matrix called Z starting at 4 and increasing to 10 in steps of 2.

```{r}
Z<- matrix(seq(4,10,by = 2),2,2)
Z
```

5.5 Compute the transpose of Y and Z with funcition t().

```{r}
t(Y)
t(Z)
```

5.6 [Matrix sums]Now compute the matrix sums Y + Z and Y + Z. The result in both cases should be the same.

```{r}
Y+Z
Z+Y
```

5.7 [Matrix multiplication] Use R to compute the matrix products YZ and ZY.

```{r}
Y%*%Z
Z%*%Y
```

5.8 Use R to compute the matrix product Y X. What happens if you attempt to compute the matrix product XY ?

```{r}
Y%*%X
```

X is 2x3, Y is 2x2, so we can't obtain the result of YX.

5.9 [Matrix element-wise multiplication]Use R to compute the element-wise matrix products Y·Z and Y·Z.

```{r}
Y*Z
Z*Y
```

5.10 [Matrix inverse]Compute the matrix inverse Y−1 via the solve() function.

```{r}
solve(Y)
Y%*%solve(Y)
solve(Y)%*%X
```

5.11 Can you do this (obtain the results of Y−1X) without first computing Y−1?

```{r}
solve(Y,X)
```

## Q6 Writing a function within R

Within your script create a short function called myFirstRFunc which takes in a single numerical argument n and outputs the sum of all those numbers strictly below n which are divisible by either 2 or 7 or both.

```{r}
myFirstRFunc<- function(n)
  {
  #Function which takes in a single numerical argument n and outputs the sum of all those numbers strictly below n which are divisible by either 2 or 7 or both.
  sum<- 0
  for(i in 1:n-1)#i is btween 1 and n, and below n.
    {
    if(i%%2==0||i%%7==0)#is i divisible by either 2 and 7 or both
      {
      sum<- sum+i
      }
    }
  return(sum)
  }
myFirstRFunc(14)
myFirstRFunc(1000)
```

## Q7 Wave plot

7.1 Define a vector called x consisting of a sequence which starts at 0 and goes to 20 in increments of 0.01.

```{r}
x<- seq(0,20,by = 0.01)
```

7.2 Next create a vector called y, which is of the same length as x, such that the ith entry of y is equal to the sin function of the ith entry of x.

```{r}
y<- sin(x)
```

7.3 Then create a data frame called sin df with two columns: x and y. You can inspect the first few rows of your data frame with the head() function.

```{r}
sin_df<- data.frame(x,y)
head(sin_df,3)
```

7.4 Write a statement to plot sin df.

```{r}
plot(sin_df)
```

7.5 Insert the following mathematical formula into your Markdown file.

$$sin^{2}(x)+cos^{2}(x)=1\tag{1.1}$$

$$\sin(x)=\sum_{n=1}^{\infty}(-1)^{n+1}\cdot \frac{x^{2n-1}}{(2n-1)!}
\approx x-\frac{x^3}{3!}+\frac{x^5}{5!}-\frac{x^7}{7!}\ldots.\tag{1.2} $$

$$ A=\left(\begin{matrix} a_{11} & a_{12}\\ a_{21} & a_{22} \end{matrix}\right). $$
